\newpage
\begin{thebibliography}{99}

\bibitem{kalman1960}
Kalman, R. E. (1960). \textit{A New Approach to Linear Filtering and Prediction Problems}. Journal of Basic Engineering, 82(1), 35-45.

\bibitem{julier1997}
Julier, S. J., \& Uhlmann, J. K. (1997). \textit{New extension of the Kalman filter to nonlinear systems}. In Signal processing, sensor fusion, and target recognition VI (Vol. 3068, pp. 182-193). SPIE.

\bibitem{wan2000}
Wan, E. A., \& Van Der Merwe, R. (2000). \textit{The unscented Kalman filter for nonlinear estimation}. In Proceedings of the IEEE 2000 Adaptive Systems for Signal Processing, Communications, and Control Symposium (pp. 153-158). IEEE.

\bibitem{li2003}
Li, X. R., \& Jilkov, V. P. (2003). \textit{Survey of maneuvering target tracking. Part I: Dynamic models}. IEEE Transactions on aerospace and electronic systems, 39(4), 1333-1364.

\bibitem{gustafsson2002}
Gustafsson, F., Gunnarsson, F., Bergman, N., Forssell, U., Jansson, J., Karlsson, R., \& Nordlund, P. J. (2002). \textit{Particle filters for positioning, navigation, and tracking}. IEEE Transactions on signal processing, 50(2), 425-437.

\bibitem{bar2001}
Bar-Shalom, Y., Li, X. R., \& Kirubarajan, T. (2001). \textit{Estimation with applications to tracking and navigation: theory algorithms and software}. John Wiley \& Sons.

\bibitem{bishop2001}
Bishop, A. N., Fidan, B., Anderson, B. D., Doğançay, K., \& Pathirana, P. N. (2010). \textit{Optimality analysis of sensor-target localization geometries}. Automatica, 46(3), 479-492.

\bibitem{sarkka2013}
Särkkä, S. (2013). \textit{Bayesian filtering and smoothing} (Vol. 3). Cambridge university press.

\bibitem{simon2006}
Simon, D. (2006). \textit{Optimal state estimation: Kalman, H infinity, and nonlinear approaches}. John Wiley \& Sons.

\bibitem{ristic2004}
Ristic, B., Arulampalam, S., \& Gordon, N. (2004). \textit{Beyond the Kalman filter: Particle filters for tracking applications}. Artech house.

\bibitem{pallotta2013}
Pallotta, G., Vespe, M., \& Bryan, K. (2013). \textit{Vessel pattern knowledge discovery from AIS data: A framework for anomaly detection and route prediction}. Entropy, 15(6), 2218-2245.

\bibitem{perera2012}
Perera, L. P., Oliveira, P., \& Guedes Soares, C. (2012). \textit{Maritime traffic monitoring based on vessel detection, tracking, state estimation, and trajectory prediction}. IEEE Transactions on Intelligent Transportation Systems, 13(3), 1188-1200.

\bibitem{fossen2011}
Fossen, T. I. (2011). \textit{Handbook of marine craft hydrodynamics and motion control}. John Wiley \& Sons.

\bibitem{xilinx2020}
Xilinx. (2020). \textit{UltraScale Architecture DSP Slice User Guide}. UG579 (v1.11).

\bibitem{altera2016}
Intel (Altera). (2016). \textit{Floating-Point IP Cores User Guide}. UG-01058.

\bibitem{numpy}
Harris, C. R., et al. (2020). \textit{Array programming with NumPy}. Nature, 585(7825), 357-362.

\bibitem{pandas}
McKinney, W. (2010). \textit{Data structures for statistical computing in python}. In Proceedings of the 9th Python in Science Conference (Vol. 445, pp. 51-56).

\bibitem{matplotlib}
Hunter, J. D. (2007). \textit{Matplotlib: A 2D graphics environment}. Computing in science \& engineering, 9(3), 90-95.

\bibitem{ais_standard}
International Maritime Organization. (2015). \textit{Revised guidelines for the onboard operational use of shipborne automatic identification systems (AIS)}. SN.1/Circ.227.

\bibitem{schubert2008}
Schubert, E., et al. (2008). \textit{Comparison and evaluation of advanced motion models for vehicle tracking}. In 2008 11th International Conference on Information Fusion (pp. 1-6). IEEE.

\end{thebibliography}
